\documentclass{article}
\begin{document}
\title{A RESEARCH REPORT ON BAKING A BIRTHDAY CAKE}
\maketitle


\section{ Abstract}

{The objective of this research was to nd out the procedures taken in order to bake a birthday cake. Many people wish to make their own cakes rather than buy them but cannot due to what they think is a tedious process involved.In my report, I break down the involved steps for making a birthday cake.}
\section{ Introduction}
{Cakes are one of the most intriguing desserts in the world, because they come in various shapes, flavors, and tastes. They are great to do for someone's birthday, an anniversary, a dessert, or just to surprise someone with a treat. Well, here is how to make a simple birthday cake. All you'll need is a little time, love, and a few items from the grocery store.}

\section{ Methodology}
{The ingredients and equipment needed are, a boxed cake mix, shortening, eggs,
oil, milk, sugar, vanilla  flavor (or another  flavor of your choice) ready to use.icing sugar and birthday candles. Then, the measuring utensils; measuring cup, mixing bowl, a cake mixer, a spatula, measuring spoons, and a round baking pan. }
\subsection{Procedures}
{Gather all of our equipment and food items in the work area, organize them according to the order we will use them in making the cake. Be sure to preheat your oven to the appropriate temperature before you begin. Start by pouring the dry cake mix into the large mixing bowl. Then, add the suitable amount of water, oil, milk, sugar, vanilla  flavor and eggs into the mix. With the electric mixer, mix the batter until it is smooth and free of clumps. Next, grease the large cake pan with the shortening. Flour the pan lightly and pour the cake batter into the cake pan, using the rubber spatula to scrape all of the batter off of the sides of the bowl. Next, place the cake into the oven and bake for thirty minutes. After the cake is done remove it from the oven. Turn off the oven and let the cake cool. After the cake has had ample time to cool, you are ready to spread the icing on the cake. If you use a spatula, rather than a knife, the icing will spread easier and will be less likely to ruin the cake. When the icing is on the cake, place the appropriate number of birthday candles on it, you are ready to present your simple birthday cake. There you have it, a birthday cake that someone will be glad to devour. This cake is easy to make, but still shows someone you}

\section {Conclusion}
{In conclusion, baking a birthday cake is a simple procedure and requires less
efforts if everything needed in the baking process is well handled.}

\author{
\large{Wabuluka Davies}
\large{15/U/13575/PS}
\large{215009779}






\end{document}